---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw5package

<!-- badges: start -->
<!-- badges: end -->

The goal of hw5package is to calculate the third length of a right triangle 
given other two sides, and calculate the trimmed mean of a vector.

## Installation

You can install the development version of hw5package like so:

``` r
install.packages(hw5package)
```

## Example
The function f1Pythagorean() is very flexible.It can 
calculate value when you give $a$ and $b$, or $a$ and $c$, or $b$ and $c$.
For example, if you input the length of two sides of the right triangle, $a=3$,
$b=4$, it return the length of hypotenuse, which is $5$.

The function f2trimmed_mean() is used for calculating the mean of a vector, 
ignoring the $s$ smallest values and $l$ largest values.
This is a basic example which shows you how to use function f2trimmed_mean():

```{r example}
library(hw5package)
f2trimmed_mean(c(1,7,3,2,5,0.5,9,10),1,2)
```
